\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-09-06 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
modification .tex partie modele

As detailed below, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. This drives us to estimate international transport costs at the 3-digit classification level, exploiting heterogeneity between products at the SITC-5 classification level. Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin. We ensure the robustness of these results by conducting two types of alternative estimates: \textit{i,} within each 3-digit sector, exploiting heterogeneity between HS-10 products. Notice that this can be done from 1989 onwards for which HS-10 data are available; \textit{ii,} running the estimation at the 4-digit sector level (still with 5-digit products) for some selected years. The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2019. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. However, we obtain no substantial difference between the results obtained for the benchmark 3-5 sector-product classification levels and those considering either the 3-10 and 4-5 ones (See Appendix \ref{app:4digit}. \textbf{JH: WHERE ARE THE 3-10/4-5 ESTIMATES? NOT IN ANY APPENDICES.}

@@

Following \cite{melitz} and the subsequent literature, we ensure selection on the export market, i.e. such that $\varphi_x^\ast > \varphi^\ast$. Making use of Equation (\ref{eq:link_thresholds}), this condition writes down as $\tau+ t\varphi^\ast_x  \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} >1$. Notice that, due to additive costs ($t>0$), this condition depends on the general equilibrium of the model (through $\varphi^\ast_x $) and cannot be imposed ex-ante by an appropriate restriction on the space parameter. We check this condition holds numerically in solving the model.

>>>>

As detailed below, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. This drives us to estimate international transport costs at the 3-digit classification level, exploiting heterogeneity between products at the SITC-5 classification level. Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin. We ensure the robustness of these results by conducting two types of alternative estimates: \textit{i,} within each 3-digit sector, exploiting heterogeneity between HS-10 products. Notice that this can be done from 1989 onwards for which HS-10 data are available; \textit{ii,} running the estimation at the 4-digit sector level (still with 5-digit products) for some selected years. The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2019. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. However, we obtain no substantial difference between the results obtained for the benchmark 3-5 sector-product classification levels and those considering either the 3-10 and 4-5 ones (See Appendix \ref{app:4digit}. \textbf{JH: WHERE ARE THE 3-10/4-5 ESTIMATES? NOT IN ANY APPENDICES.}
 \textbf{XXXX-GD:4-5 ESTIMATES are in table 1. 3-10 I am not sure... On y fait allusion dans la procédure en IV, c’est sûr.}

@@

Following \cite{melitz} and the subsequent literature, we ensure selection on the export market, i.e. such that $\varphi_x^\ast > \varphi^\ast$. Making use of Equation (\ref{eq:link_thresholds}), this condition writes down as $\left[\tau+ t\varphi^\ast_x \right] \left( \frac{f}{f_x} \right)^{\frac{1}{1-\sigma}} >1$. Two comments can be made at this point. First, additive costs ($t>0$) make the selection condition more likely to happen everything else equal for any given values of ad-valorem and fixed costs. Put differently, additive costs somehow relax the constraint of the fixed cost of exporting. Second, and most importantly, due to additive costs ($t>0$), the export selection condition depends on the general equilibrium of the model (through $\varphi^\ast_x $) and cannot be imposed ex-ante by an appropriate restriction on the space parameter. We check this condition holds numerically in solving the model.\footnote{This is no longer the case under ad-valorem costs only. In this case, with $t=0$, we find the usual condition that $\phi^\ast_x >\phi^\ast$ iif $\tau^{\sigma-1}\frac{f_x}{f}>1$.}
